\chapter{FASTQ tools}
\label{fastq}

The toolkit has a set of tools dedicated to manipulate FASTQ files. Some of these tools allow the data conversion to/from different formats, e.g., there are tools designed to convert a FASTQ file into a sequence or a FASTA/Multi-FASTA format, or converting DNA in some of those formats to FASTQ.

Furthermore, there are tools for data manipulation in this format, which are designed to exclude 'N', remove low quality scored reads, following different metrics and randomize DNA sequences. Succeeding the manipulation, it is also possible to perform analyses over these files, simulations and mutations. The current available tools for FASTQ format analysis and manipulation include:

\begin{enumerate}

\item \texttt{gto\char`_fastq\char`_to\char`_fasta}: to convert a FASTQ file format to a pseudo FASTA file.

\item \texttt{gto\char`_fastq\char`_to\char`_mfasta}: to convert a FASTQ file format to a pseudo Multi-FASTA file.

\item \texttt{gto\char`_fastq\char`_exclude\char`_n}: to discard the FASTQ reads with the minimum number of "N" symbols.

\item \texttt{gto\char`_fastq\char`_extract\char`_quality\char`_scores}: to extract all quality-scores from FASTQ reads.

\item \texttt{gto\char`_fastq\char`_info}: to analyse the basic information of FASTQ file format.

\item \texttt{gto\char`_fastq\char`_maximum\char`_read\char`_size}: to filter FASTQ reads with length higher than the value defined.

\item \texttt{gto\char`_fastq\char`_minimum\char`_quality\char`_score}: to discards reads with average quality-score below the value defined.

\item \texttt{gto\char`_fastq\char`_minimum\char`_read\char`_size}: to filter the FASTQ reads with length smaller than the value defined.

\item \texttt{gto\char`_fastq\char`_rand\char`_extra\char`_chars}: to substitute in the DNA sequence of the FASTQ files the outside ACGT chars by random ACGT symbols.

\item \texttt{gto\char`_fastq\char`_from\char`_seq}: to convert a genomic sequence to pseudo FASTQ file format.

\item \texttt{gto\char`_fastq\char`_mutate}: to create a synthetic mutation of a FASTQ file given specific rates of mutations, deletions and additions.

\item \texttt{gto\char`_fastq\char`_split}: to split Paired End files according to the direction of the strand ('/1' or '/2').

\item \texttt{gto\char`_fastq\char`_pack}: to package each FASTQ read in a single line.

\item \texttt{gto\char`_fastq\char`_unpack}: to unpack the FASTQ reads packaged using the \texttt{gto\char`_fastq\char`_pack} tool.

\item \texttt{gto\char`_fastq\char`_quality\char`_score\char`_info}: to analyse the quality-scores of a FASTQ file.

\item \texttt{gto\char`_fastq\char`_quality\char`_score\char`_min}: to analyse the minimal quality-scores of a FASTQ file.

\item \texttt{gto\char`_fastq\char`_quality\char`_score\char`_max}: to analyse the maximal quality-scores of a FASTQ file.

\item \texttt{gto\char`_fastq\char`_cut}: to cut read sequences in a FASTQ file. 

\item \texttt{gto\char`_fastq\char`_minimum\char`_local\char`_quality\char`_score\char`_forward}: to filter reads considering the quality score average of a defined window size of bases.

\item \texttt{gto\char`_fastq\char`_minimum\char`_local\char`_quality\char`_score\char`_reverse}: to filters reverse reads, considering the average window size score defined by the bases.

\item \texttt{gto\char`_fastq\char`_xs}: is a skilled FASTQ read simulation tool, flexible, portable and tunable in terms of sequence complexity.

\item \texttt{gto\char`_fastq\char`_clust\char`_reads}: to group reads and create an index file.

\item \texttt{gto\char`_fastq\char`_complement}: to replace ACGT bases with their complements in a FASTQ file format.

\item \texttt{gto\char`_fastq\char`_reverse}: to reverse ACGT bases order for each read in a FASTQ file format.

\item \texttt{gto\char`_fastq\char`_variation\char`_map}: to identify the variation that occurs in sequences corresponding to the reads or a set of reads.

\item \texttt{gto\char`_fastq\char`_variation\char`_filter}: to filter and segment the regions of singularity from the output of \texttt{gto\char`_fastq\char`_variation\char`_map}.

\item \texttt{gto\char`_fastq\char`_variation\char`_visual}: to depict the regions of singularity using the output from \texttt{gto\char`_fastq\char`_variation\char`_filter} into an SVG image.

\item \texttt{gto\char`_fastq\char`_falcon}: to measures the similarity between any FASTQ file, independently from the size, against any multi-FASTA database.

\end{enumerate}

\input{\FASTQToolsPath/FastqToFasta.tex}
\input{\FASTQToolsPath/FastqToMFasta.tex}
\input{\FASTQToolsPath/FastqExcludeN.tex}
\input{\FASTQToolsPath/FastqExtractQualityScores.tex}
\input{\FASTQToolsPath/FastqInfo.tex}
\input{\FASTQToolsPath/FastqMaximumReadSize.tex}
\input{\FASTQToolsPath/FastqMinimumQualityScore.tex}
\input{\FASTQToolsPath/FastqMinimumReadSize.tex}
\input{\FASTQToolsPath/FastqRandExtraChars.tex}
\input{\FASTQToolsPath/FastqFromSeq.tex}
\input{\FASTQToolsPath/FastqMutate.tex}
\input{\FASTQToolsPath/FastqSplit.tex}
\input{\FASTQToolsPath/FastqPack.tex}
\input{\FASTQToolsPath/FastqUnpack.tex}
\input{\FASTQToolsPath/FastqQualityScoreInfo.tex}
\input{\FASTQToolsPath/FastqQualityScoreMax.tex}
\input{\FASTQToolsPath/FastqQualityScoreMin.tex}
\input{\FASTQToolsPath/FastqCut.tex}
\input{\FASTQToolsPath/FastqMinimumQualityScoreForward.tex}
\input{\FASTQToolsPath/FastqMinimumQualityScoreReverse.tex}
\input{\FASTQToolsPath/FastqXS.tex}
\input{\FASTQToolsPath/FastqClustReads.tex}
\input{\FASTQToolsPath/FastqComplement.tex}
\input{\FASTQToolsPath/FastqReverse.tex}
\input{\FASTQToolsPath/FastqVariationMap.tex}
\input{\FASTQToolsPath/FastqVariationFilter.tex}
\input{\FASTQToolsPath/FastqVariationVisual.tex}
\input{\FASTQToolsPath/FastqMetagenomics.tex}
