\chapter{General purpose tools}
\label{seq}
The toolkit has also a set of tools with a more general-purpose, which were not designed to work with a specific data format. Instead, this set of tools was developed as an auxiliary component to help in the construction of pipelines combining all the subsets described. This set contains tools for char manipulations, such as reversing, segmentation and permutation; for manipulating numerical scores, such sum, filter, min and max calculation of a numeric matrix mainly originated from the tools' outputs. Currently, the tools available for general purposes are:
\begin{enumerate}

\item \texttt{gto\char`_char\char`_to\char`_line}: to split a sequence into lines, creating an output sequence which has a char in each line.

\item \texttt{gto\char`_new\char`_line\char`_on\char`_new\char`_x}: to split different rows with a new empty line separating rows with different values.

\item \texttt{gto\char`_upper\char`_bound}: to set an upper bound in a file with one numerical value per line.

\item \texttt{gto\char`_lower\char`_bound}: to set a lower bound in a file with one numerical value per line.

\item \texttt{gto\char`_brute\char`_force\char`_string}: to generate all combinations, line by line, for an inputted alphabet and specific size.

\item \texttt{gto\char`_real\char`_to\char`_binary\char`_with\char`_threshold}: to convert a sequence of real numbers into a binary sequence, given a threshold.

\item \texttt{gto\char`_sum}: to add decimal values from a file, line by line, split by spaces or tabs.

\item \texttt{gto\char`_filter}: to filters numerical sequences.

\item \texttt{gto\char`_word\char`_search}: to search for a word in a file.

\item \texttt{gto\char`_permute\char`_by\char`_blocks}: to permute by block sequence, FASTA and Multi-FASTA files. 

\item \texttt{gto\char`_info}: to obtain the basic properties of a file, namely size, cardinality, distribution percentage of the symbols, among others.

\item \texttt{gto\char`_segment}: to segment a filtered sequence.

\item \texttt{gto\char`_comparative\char`_map}: to create a visualization for comparative maps.

\item \texttt{gto\char`_max}: to compute the maximum value in each row between two files.

\item \texttt{gto\char`_min}: to compute the minimum value in each row between two files.

\end{enumerate}

\input{\GeneralPurposeToolsPath/CharToLine.tex}
\input{\GeneralPurposeToolsPath/NewLineForNewValue.tex}
\input{\GeneralPurposeToolsPath/UpperBound.tex}
\input{\GeneralPurposeToolsPath/LowerBound.tex}
\input{\GeneralPurposeToolsPath/BruteForceString.tex}
\input{\GeneralPurposeToolsPath/RealToBinaryWithThreshold.tex}
\input{\GeneralPurposeToolsPath/Sum.tex}
\input{\GeneralPurposeToolsPath/Filter.tex}
\input{\GeneralPurposeToolsPath/WordSearch.tex}
\input{\GeneralPurposeToolsPath/PermuteByBlocks.tex}
\input{\GeneralPurposeToolsPath/Info.tex}
\input{\GeneralPurposeToolsPath/Segment.tex}
\input{\GeneralPurposeToolsPath/ComparativeMap.tex}
\input{\GeneralPurposeToolsPath/Max.tex}
\input{\GeneralPurposeToolsPath/Min.tex}
