\chapter{Amino acid sequence tools}
%\addcontentsline{toc}{chapter}{Sequence tools}
\label{seq}
A more specific subset of tools is the Amino Acid Sequence tools, designed to manipulate amino acid sequences. The main features of those tools are grouping sequences, for instance by their properties, such as electric charge (positive and negative), uncharged side chains, hydrophobic side chains and special cases. It is also possible generating pseudo-DNA with characteristics passed by amino acid sequences, or for data compression, using cooperation between multiple contexts and substitutional tolerant context models. The current available amino acid sequence tools, for analysis and manipulation, are:
\begin{enumerate}
	
\item \texttt{gto\char`_amino\char`_acid\char`_to\char`_group}: it converts an amino acid sequence to a group sequence.

\item \texttt{gto\char`_amino\char`_acid\char`_to\char`_pseudo\char`_dna}: it converts an amino acid (protein) sequence to a pseudo DNA sequence.

\item \texttt{gto\char`_amino\char`_acid\char`_compressor}: it is a new lossless compressor to compress efficiently amino acid sequences (proteins).

\item \texttt{gto\char`_amino\char`_acid\char`_from\char`_fasta}: it converts DNA sequences in FASTA or Multi-FASTA file format to an amino acid sequence.

\item \texttt{gto\char`_amino\char`_acid\char`_from\char`_fastq}: it converts DNA sequences in the FASTQ file format to an amino acid sequence.

\item \texttt{gto\char`_amino\char`_acid\char`_from\char`_seq}: it converts DNA sequences to an amino acid sequence.

%\item \texttt{gto\char`_amino\char`_acid\char`_to\char`_seq}: it converts amino acid sequences to DNA sequences.

\end{enumerate}

\input{\AminoAcidSequenceToolsPath/AminoAcidToGroup.tex}
\input{\AminoAcidSequenceToolsPath/AminoAcidToPseudoDNA.tex}
\input{\AminoAcidSequenceToolsPath/AminoAcidCompressor.tex}
\input{\AminoAcidSequenceToolsPath/AminoAcidFromFasta.tex}
\input{\AminoAcidSequenceToolsPath/AminoAcidFromFastq.tex}
\input{\AminoAcidSequenceToolsPath/AminoAcidFromSeq.tex}
%\input{\AminoAcidSequenceToolsPath/AminoAcidToSeq.tex}
